Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2013-11-13 limits/ms.tex
New sigp plots and updated tex.

\begin{figure*}
\includegraphics[width=0.33\textwidth]{MockGalProfile-a.pdf} 
\includegraphics[width=0.33\textwidth]{MockGalProfile-b.pdf} 
\includegraphics[width=0.33\textwidth]{MockGalProfile-c.pdf}
\caption{{\bf JR. Cut the analytic profiles from this Figure. All fonts and labels should be larger. Left panel should start at 0.7kpc.}
\textbf{Left:} 
Spherically averaged density profiles of the four mock galaxies showing the stellar (dotted), dark matter (dashed),
and total (solid) densities. Notice that the stars in models Sdom/DMshallow and Sdom/DMcuspy contribute significantly to the central potential. 
\textbf{Middle:} 
The radially averaged two-dimensional projected density.
The critical density for lensing at $z_L=0.31$, $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$, is marked by the horizontal line. 
\textbf{Right:}
The enclosed projected mass.
}
\label{mock galaxies}
\end{figure*}

@@

\section{Results}\label{sec:results}
\figref{reconstruction} shows a typical reconstruction of a
lens. The far left plot shows the ensemble average arrival time surface with
image marked as circles and the inferred source position as a diamond. The
center plot shows the radial density profile. The error bars cover the full
range of models generated by \Glass {\bf JR. Why do this? Surely 1 or 2 sigma
errors make more sense? I've deleted the ``full ensemble'' results and kept the
$1\sigma$ ones instead.}. The true density profile from the mock data is also
plotted for comparison. The vertical lines mark the radial position of the
images. The final plot on the right is of the enclosed mass. As expected, the
error bars are smallest in the region of the images where the most information
about the lens is present. The dip in the profile at the end of the profile is
due to the cut off in mass in the lensing map. This is of little importance,
though, as there is no lensing information there.

@@

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-a.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
\caption{ {\bf (Left)} Mock data distribution on coarse grid. {\bf (Right)} Recover ensemble average kappa distribution.}
\label{2d mass reconstruction}
\end{figure*}

%
\begin{equation} \label{badness}
  f_r = \frac {\int \left|\Delta M(r)\right|\; dr } {\int M(r)\; dr}
\end{equation}
%
while in \figref{main results pixel-wise} the quality is defined over all the pixels
%
\begin{equation} \label{badness}
f_\theta = \frac
       {\int \left|\Delta M(\vec\theta)\right| \; d \vec{\theta} }
       {\int M(\vec\theta) \; d \vec\theta}
\end{equation}
In both cases, the delta difference is between a single recovered model and the known mock galaxy.
%\begin{equation}
%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
%\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
%\end{equation}
%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.

@@

\begin{figure*}
\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sb.pdf}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sb.pdf}
\caption{ 
(Left) Projected radially averaged velocity dispersion for Sdom/DMcuspy ZConstrastR1R3 models and the mock data.
(Right) Projected radially averaged velocity dispersion for Sdom/DMcuspy QuadR1a models and the mock data.
}
\label{main results pixel-wise}
\end{figure*}

@@

\item \sout{Take a model that is well constrained by strong lensing
  (e.g. quad with time delays). Calculate $\sigma_p(R)$ for each model
  in the ensemble using the kinematics module. Compare this with the
true $\sigma_p(R)$ from the mock data} to obtain a $\chi^2$ (actually
  a $\chi^2$ this time!).  \sout{Show the true $\sigma_p(R)$ and overlay
  coloured bands from the lensing model ensemble assuming $\beta = 0$
or $\beta = 1$.}

@@

\item Clarify number of lens configurations in \S\ref{sec:lensconfig}.

>>>>

\begin{figure*}
\includegraphics[width=0.33\textwidth]{MockGalProfile-a.pdf} 
\includegraphics[width=0.33\textwidth]{MockGalProfile-b.pdf} 
\includegraphics[width=0.33\textwidth]{MockGalProfile-c.pdf}
\caption{{\bf JR. \sout{Cut the analytic profiles from this Figure. All fonts and labels should be larger.} Left panel should start at 0.7kpc.}
\textbf{Left:} 
Spherically averaged density profiles of the four mock galaxies showing the stellar (dotted), dark matter (dashed),
and total (solid) densities. Notice that the stars in models Sdom/DMshallow and Sdom/DMcuspy contribute significantly to the central potential. 
\textbf{Middle:} 
The radially averaged two-dimensional projected density.
The critical density for lensing at $z_L=0.31$, $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$, is marked by the horizontal line. 
\textbf{Right:}
The enclosed projected mass.
}
\label{mock galaxies}
\end{figure*}

@@

\section{Results}\label{sec:results}
\figref{reconstruction} shows a typical reconstruction of a lens. The far left
plot shows the ensemble average arrival time surface with image marked as
circles and the inferred source position as a diamond. The center plot shows
the radial density profile. The error bars cover a $1\sigma$ range around the
median. \sout{the full range of models generated by \Glass {\bf JR. Why do
this? Surely 1 or 2 sigma errors make more sense? I've deleted the ``full
ensemble'' results and kept the $1\sigma$ ones instead.}}. The true density
profile from the mock data is also plotted for comparison. The vertical lines
mark the radial position of the images. The final plot on the right is of the
enclosed mass. As expected, the error bars are smallest in the region of the
images where the most information about the lens is present. The dip in the
profile at the end of the profile is due to the cut off in mass in the
lensing map. This is of little importance, though, as there is no lensing
information there.

@@

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-a.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
\caption{ {\bf (Left)} Mock data distribution on coarse grid for Sdom/DMcuspy. {\bf (Right)} Recover ensemble average kappa distribution.}
\label{2d mass reconstruction}
\end{figure*}

The main results from modeling these different configurations are shown in
\figref{main results} and \figref{main results pixel-wise}. Each
subplot corresponds to a different mock galaxy. We show the fractional error of the mass
distribution for each of the test configurations with (red) and without stellar mass (black)
In \figref{main results}, the error is defined over radial bins of mass as
%
\begin{equation} \label{badness}
  f_R = \frac {\sum_r \left|M_p(r) - \tilde M_p(r)\right| } {\sum \tilde M_p(r)}
\end{equation}
%
where $M_p$ is the mass in a radial bin and $\tilde M_p$ is the mass from the mock galaxy.
In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$
%
\begin{equation} \label{badness}
f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \tilde M(\vec\theta)\right| } {\sum \tilde M(\vec\theta)}
\end{equation}
%
%\begin{equation}
%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
%\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
%\end{equation}
%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.

@@

\begin{figure*}
\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sb.pdf}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sb.pdf}
\caption{Estimated projected radially averaged velocity dispersion $\sigma_p$ for two Sdom/DMcuspy models ZConstastR1R3
  (left) and QuadR1a (right) assuming an anisotropy $B=0$ (green) and $B=0$ (blue). In both plots, the actual projected
  velocity dispersion of the mock data (black).
  }
\label{fig:sigp}
\end{figure*}

@@

\item \sout{Take a model that is well constrained by strong lensing
  (e.g. quad with time delays). Calculate $\sigma_p(R)$ for each model
  in the ensemble using the kinematics module. Compare this with the
true $\sigma_p(R)$ from the mock data to obtain a $\chi^2$ (actually
  a $\chi^2$ this time!). Show the true $\sigma_p(R)$ and overlay
  coloured bands from the lensing model ensemble assuming $\beta = 0$
or $\beta = 1$.}

@@

\item \sout{Clarify number of lens configurations in \S\ref{sec:lensconfig}.}
